Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-08-26 snapshot_system/arch.tex
revise

In a busy VM cluster, snapshot deletions are as frequent as snapshot creations.
However, data deduplication complicates the deletion process because space saving relies on the sharing of data,
thus making it difficult to decide which chunks are safe to delete.
In a traditional deduplication system, deletion often require looking at global scope to
resolve the data dependency between logical backup entities and physical data chunks.
Our VM-centric snapshot storage design simplifies the deletion process since 
we only need to locate unreferenced chunks within each VM's snapshot store to free up space when deleting a snapshot.
The PDS data chunks are commonly shared all VMs and we do not consider their reference
counting during snapshot deletion.
%The selection of PDS data chunks is updated periodically independent of snapshot deletion process.

While we can use the mark-and-sweep technique~\cite{Guo2011}, 
it still takes significant time to conduct this process every time there is a snapshot deletion.
In the case of Alibaba, snapshot backup is conducted automatically and there are 
about 10 snapshot stored for every user. When there is
a new snapshot created every day,  there will be  a snapshot expired everyday to maintain
a balanced storage use. Given the large number of snapshot deletion requests, we seek
a fast solution with a very low resource usage to delete snapshots.

With this in mind, we develop an {\em approximate} deletion strategy to trade deletion accuracy for
speed and resource usage. Our method sacrifices a small percent of storage leakage
to effectively identify unused chunks in $O(n)$ time, with $n$ being the logical number of non-PDS chunks 
to be deleted from a VM snapshot store.
The algorithm contains three aspects.

>>>>

In a busy VM cluster, snapshot deletions can occur frequently.
Deduplication complicates the deletion process because space saving relies on the sharing of data
and it requires the global reference of deldted chunks to be identified before  they can be safely removed.
While we can use the mark-and-sweep technique~\cite{Guo2011}, 
it still takes significant resource to conduct this process every time there is a snapshot deletion.
In the case of Alibaba, snapshot backup is conducted automatically and there are 
about 10 snapshot stored for every user. When there is
a new snapshot created every day,  there will be  a snapshot expired everyday to maintain
a balanced storage use. Given the large number of snapshot deletion requests, we seek
a fast solution with a very low resource usage to delete snapshots.
%In a traditional deduplication system, deletion often require looking at global scope to
%resolve the data dependency between logical backup entities and physical data chunks.
Our VM-centric snapshot storage design simplifies the deletion process since 
we can focus on  unreferenced chunks within each VM.
The PDS data chunks are commonly shared all VMs and we do not consider them
during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
Another resource-saving strategy we propose is
an {\em approximate} deletion strategy to trade deletion accuracy for
speed and resource usage. Our method sacrifices a small percent of storage leakage
to efficiently identify unused chunks in $O(n)$ time, with $n$ being the logical number of non-PDS chunks 
to be deleted from a VM snapshot store.  The algorithm contains three aspects.
